Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-01-15 paper/ccvpn.tex
Text updates
More text
Updates
paper sec 4.2
first draft of sec analysis section (5)
better plot ins experiments section
updated paper
abstract

\documentclass[conference]{sig-alternate-05-2015}

\usepackage{todonotes,times,amssymb,amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{multirow,paralist}
\usepackage{fancybox}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color, colortbl}
\usepackage{transparent}
\usepackage{balance}
\usepackage{url}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amssymb, framed, graphics}
\usepackage{bytefield}
\usepackage[group-separator={,}]{siunitx}
\usepackage[underline=true]{pgf-umlsd}
\usepackage{hyphenat}
\usepackage{cite}
\usepackage{fancybox,fancyvrb}
\usepackage{url}
\usepackage{framed}
\usepackage{xspace}
\usepackage{listings}
\usepackage{array}
\usepackage{threeparttable}

\makeatletter
\makeatother

\newcommand{\ccnname}[1]{\path{#1}}
\newcommand{\Adv}{{\sf Adv}}
\newcommand{\mAdv}{\mathsf{Adv}}
\newcommand{\advc}{{\sf Adv}$^C$}
\newcommand{\madvc}{\mathsf{Adv}^C}
\newcommand{\advl}{{\sf Adv}$^L$}
\newcommand{\madvl}{\mathsf{Adv}^L}
\newcommand{\advi}{{\sf Adv}$^I$}
\newcommand{\madvi}{\mathsf{Adv}^I}
\newcommand{\adve}{{\sf Adv}$_E$}
\newcommand{\advo}{{\sf Adv}$_O$}
\newcommand{\advd}{{\sf Adv}$_D$}
\newcommand{\NN}{\bar{N}}

\makeatletter
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
\makeatother
\mathchardef\mhyphen="2D
\newcommand{\E}[1]{\mathrm{E} #1}
\newcommand{\NE}[1]{\mathrm{E}\mhyphen #1}

\newcolumntype{!}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{N}{@{}m{0pt}@{}}

%\newtheorem{proof}{\textbf{Proof}}
\newtheorem{defn}{\textbf{Definition}}
\newtheorem{define}{\textbf{Definition}}
\newtheorem{thm}{\textbf{Theorem}}
\newtheorem{cor}{\textbf{Corollary}}
\newtheorem{lemma}{\textbf{Lemma}}

\newcolumntype{!}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{N}{@{}m{0pt}@{}}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\title{Tunneling in Content Centric Networks}
\numberofauthors{1}
\author{
\alignauthor
%Cesar Ghali \quad Gene Tsudik \quad Christopher A. Wood\titlenote{Supported by the NSF Graduate Research Fellowship DGE-1321846.}\\
%       \affaddr{Computer Science Department, University of California Irvine}\\
%       \email{\{cghali, gene.tsudik, woodc1\}@uci.edu}
}

\maketitle
\pagestyle{plain}

\begin{abstract}
TODO
\end{abstract}

% meat and potatoes
%\input{01-introduction}

%\section{Conclusion and Future Work} \label{sec:conclusion}

\bibliographystyle{abbrv}
\bibliography{references}

>>>>

\documentclass[conference,letterpaper,10pt]{IEEEtran}
\usepackage{blindtext, graphicx, url, paralist}

% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

\usepackage{microtype}

\usepackage[tight,footnotesize]{subfigure}
\usepackage{fixltx2e}

\usepackage{multirow}

\usepackage{algorithm2e}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

\hyphenation{op-tical net-works semi-conduc-tor}

\newtheorem{definition}{\textbf{Definition}}[section]
\newtheorem{theorem}{\textbf{Claim}}[section]
\newtheorem{corollary}{\textbf{Corollary}}[theorem]
\newtheorem{lemma}[theorem]{\textbf{Lemma}}

@@

\title{Tunnels to Towers: Secure Virtual Private Networking for CCN}

\maketitle

\begin{abstract}
Content Centric Networking (CCN) is a future Internet architecture which is envisioned as an alternative to the current IP-based model. CCN emphasizes content distribution by making contents directly addressable in a request-based information centric network. An advantage of CCN is that it has some innate privacy friendly features, such as lack of source and destination addresses in packets. However, to be considered a viable future Internet architecture, CCN must offer services for private and anonymous communication that are at least equivalent for  to those present in the IP architecture. Among such, VPNs are a very popular application that enables users to send and receive data across shared or public networks as if their computing devices were directly connected to the same private network. In this work we design, implement and evaluate CCVPN, a content centric virtual private network capable of providing the same functionality of VPNs within the CCN Internet architecture. To the best of our knowledge CCVPN is the first proposal of a VPN alike service for CCNs. In addition to the CCVPN design, we also provide a security analysis and experimental performance evaluation for this new system.
\end{abstract}

\begin{IEEEkeywords}
%Human Mobility, Group Detection, Group Dynamics, Periodicity, Opportunistic Routing.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\input{01-introduction}
\input{02-overview}
\input{03-related}
\input{04-design}
\input{05-sec-analysis}
\input{06-perf-analysis}
\input{07-experiment}
%\input{08-security}

\section{Conclusion}\label{conclusion}
\todo{TODO}

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\tiny

\bibliographystyle{IEEEtran}
\bibliography{references}

% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{picture}}]{John Doe}
% \blindtext
% \end{IEEEbiography}
